Cartogram Mapping and its Application to Cancer Data Visualization

### 2019-09-27 review_article.Rmd
Interactivity sections

# Interactivity and Animation  {#ch:interacting}

<!-- XXX Define interactivity, define animation -->
Interactivity and animation enhance online atlases by enabling additional information to be presented in the same display. Implementing movement and allowing for changes in the display invites the viewer to engage with the display, and the information presented.

@@

## Interactivity

Interactivity can be implemented within modern mapping methods to incorporate additional information and complexity without overloading the user.
Adding too much information to a map may create cognitive overload [@mcgranaghan1993cartographic] in which the user reaches an information threshold, beyond which will not be able to make sense of the information. 
Complexity and density of visualization methods can overwhelm novice decision makers, however experts are able to use the detail more readily when making-decisions [@cliburn2002design]. 
Supplementary information can be incorporated into online atlases without cluttering the display. Interactive design features found in online cancer maps include tool tip features, drop down menus, data selection, zooming and panning.
Allowing users to explore the map for more information and providing flexibility in the display [@HTLWM]. The use of these supports were found in various online cancer maps identified by @roberts2019communication.
Additionally, interactivity allows the user to toggle between different variables, map views or multiple realizations of possible future scenarios [@goodchild1994introduction]. Thus providing additional mechanisms for the users comprehension as well as the uncertainty of the available information (@maceachren1992visualizing; @van1994visualization). For example, changing the population, age or other demographic variables.
The controls for basic interactive features are often placed outside of the plot space [@TGA], the map image is updated/replaced as the user interacts with the controls. 
Some more advanced interactions include direct interactions with the plot via the use of overlaid tool tip features, very few cancer atlases involve these more complex selection interactive capabilities.

@@

>>>>

# User interactions with maps {#ch:interacting}

Interactivity and animation enhance online atlases by enabling additional information to be presented in the same display. Implementing movement and allowing for changes in the display invites the viewer to engage with the display, and the information presented.

@@

## Interaction in publicly available atlases

Interactivity can be implemented within modern mapping methods to incorporate additional information and complexity without overloading the user.
Adding too much information to a map may create cognitive overload [@mcgranaghan1993cartographic] in which the user reaches an information threshold, beyond which will not be able to make sense of the information. 
Complexity and density of visualization methods can overwhelm novice decision makers, however experts are able to use the detail more readily when making-decisions [@cliburn2002design]. 
Supplementary information can be incorporated into online atlases without cluttering the display. Interactive design features found in online cancer maps include tool tip features, drop down menus, data selection, zooming and panning.
Allowing users to explore the map for more information and providing flexibility in the display [@HTLWM]. The use of these supports were found in various online cancer maps identified by @roberts2019communication.
Additionally, interactivity allows the user to toggle between different variables, map views or multiple realizations of possible future scenarios [@goodchild1994introduction]. Thus providing additional mechanisms for the users comprehension as well as the uncertainty of the available information [@maceachren1992visualizing, @van1994visualization]. For example, changing the population, age or other demographic variables.
The controls for basic interactive features are often placed outside of the plot space [@TGA], the map image is updated/replaced as the user interacts with the controls. 
Some more advanced interactions include direct interactions with the plot via the use of overlaid tool tip features, very few cancer atlases involve these more complex selection interactive capabilities.

@@

## Underutilized techniques
